---
---
---

## Preparation

1.Import the data and compute the daily log return.

```{r}
HSCE<-read.csv("HSCE.csv",header=TRUE) 
HSCEprices<-as.numeric(as.vector(HSCE$Adj.Close))
HSCEprices<-HSCEprices[!any(is.na(HSCEprices))]

n0=length(HSCEprices)
HSCElogprices<-log(HSCEprices)
HSCElogreturns<-HSCElogprices[2:n0]-HSCElogprices[1:(n0-1)]
```

2.Define necessary variables and functions

```{r}
#time frame:
#According to my research,
#there are 245 trading days from the end of 26 April 2020 to end of 26 April 2021.

# set 26 April 2020 as present day

S0=HSCEprices[n0] #current price
K_strike = 11638.18 # initial level, or strike price
dt=1/252 # frequency: one day

T_remain = 245*dt # time to maturity 


#define the visualization
Visualize<-function(S){
  # endindex=ncol(S)
  minS=min(S);maxS=max(S) # the y-limits of the plot
  noS<-nrow(S)
  cl<-rainbow(noS) # vector of rainbow colors
  plot(S[1,],type="l",ylim=c(minS,maxS),col=cl[1])
  if(noS>1){
    for(i in 2:noS){
      lines(S[i,],col=cl[i])
    }
  }
}
# try visualize the history data
Histdata<-matrix(rep(HSCEprices,1),ncol=n0,byrow=T);
Visualize(Histdata)

# define the simulation function 
SimGBMsde<-function(Nsim,S0,mu,sigma,Deltat,T_remain){
  m=T_remain/Deltat # number of periods
  S=matrix(S0,nrow=Nsim,ncol=m+1)
  for(i in 1:Nsim){
    Z<-rnorm(m)
    for(j in 2:(m+1)){
       # S[i,j]=S[i,j-1]+S[i,j-1]*(mu*Deltat+sigma*sqrt(Deltat)*Z[j-1])
       S[i,j]=S[i,j-1]*exp(v*Deltat+sigma*sqrt(Deltat)*Z[j-1])
    }
  }
  S
}
```

## (a)Payoff function

The payoff function is:

$V(S_t,t) = e^{-r(T-t)}\cdot E[V(S_T,T)]$

$$ = e^{-r(T-t)} \cdot 1.05D \cdot P(S_{max}(T) \geq 1.3K) \ +\ e^{-r(T-t)} \cdot D \cdot E[max(\frac{S_T}{K},1)\cdot \boldsymbol{1} \{S_{max}(T) < 1.3K\}]\ $$

where D is the denomination, D = 1000 USD. K is the initial level

```{r}
NotePayoff<-function(Spath, Denom=1000,K= K_strike){
  T = length(Spath) #the final date of simulation
  ST <- Spath[T]
  S_max_T <- max(Spath)
  payoff <- ifelse(S_max_T >= 1.3*K, 1.05 * Denom, Denom* max(ST/K ,1))
  payoff
}
```

## (b) The estimated model for the underlying asset(s) with the estimated parameters

i.  in the real world;
ii. in the risk-neutral world.

## i. we first estimate the real world model, with

$$X_{j+1} = X_j+ X_j*(v- \frac{\sigma^2}{2}) *\Delta t + X_j*\sigma \sqrt{\Delta t} Z_j$$ Where $$v = \frac{\overline{log\_returns}}{\Delta t}$$ and $$\sigma = \frac{sd(log\_returns)}{\Delta t}$$

```{r}
set.seed(2304343)
v=mean(HSCElogreturns)/dt
sigma=sd(HSCElogreturns)/sqrt(dt)
mu = v+ sigma^2/2
#Here we use 1000 simulation as a demo just for visualization
Nsim=1000
SimHSCE<-SimGBMsde(Nsim,S0,mu,sigma,dt,T_remain);
Visualize(SimHSCE)
```

## ii. Estimate in risk neutral world, with

$$X_{j+1} = X_j+ r *\Delta t + \sigma \sqrt{\Delta t} Z_j$$ Where $$r = 0.17\% $$ and $$\sigma = \frac{sd(log\_returns)}{\Delta t}$$

```{r}
set.seed(2304343)
r=0.0017
S0=HSCEprices[n0]
#Here we use 1000 simulation as a demo just for visualization
Nsim=1000
# sigma is the same as previous one
SimHSCE<-SimGBMsde(Nsim,S0,r,sigma,dt,T_remain)
Visualize(SimHSCE)
```

## (c) Estimate probabilities occurring probabilities of the scenarios at redemption (as per defined in the fact sheet) under different situation using Monte-Carlo, and risk neutral.

Based on the description of the product, there are three scenarios:

scenario 1: $$S_{max}(T) \geq 1.3S_0 $$ scenario 2:$$S_{max}(T) < 1.3S_0\ and\  S_T/S_0 > 1 $$ scenario 3:$$S_{max}(T) < 1.3S_0\ and\  S_T/S_0 \leq 1 $$

Using Monte-Carlo method $$P(scenario\ i) = \frac{\#\ of\ scenario\ i}{\#\ of\ simulation}$$

```{r}
set.seed(2304343)
Nsim = 70000
SimHSCE<-SimGBMsde(Nsim,S0,r,sigma,dt,T_remain);

S_max_T <- apply(SimHSCE, 1, max)
S_T <- SimHSCE[, ncol(SimHSCE)]
scenarios <- vector("integer", length = length(S_max_T))
for (i in 1:length(S_max_T)) {
    if (S_max_T[i] >= 1.3 * K_strike) {
       scenarios[i] <- 1
  } else if (S_max_T[i] < 1.3 * K_strike && S_T[i] / K_strike > 1) {
       scenarios[i] <- 2
  } else {
       scenarios[i] <- 3
  }
}

P_1 = sum(scenarios == 1)/Nsim;cat("probabilities of the scenario 1 is:",P_1,"\n")
P_2 = sum(scenarios == 2)/Nsim;cat("probabilities of the scenario 2 is:",P_2,"\n")
P_3 = sum(scenarios == 3)/Nsim;cat("probabilities of the scenario 3 is:",P_3,"\n")
```

## (d) Risk-neutral price

```{r}
set.seed(2304343)
Nsim=70000;
SimHSCE <- SimGBMsde(Nsim,S0,r,sigma,dt,T_remain)
SimNotes<- exp(-r*T_remain)*apply(SimHSCE,1,NotePayoff)
NoteValue=mean(SimNotes); NoteValueVar=var(SimNotes)/Nsim
cat("Noteprice is",NoteValue,"\n")
cat("95% confidence interval of price is",NoteValue-1.96*sqrt(NoteValueVar),NoteValue+1.96*sqrt(NoteValueVar))
```

## (e&f) Simulating Delta and Gamma

```{r}
set.seed(2304343)
SimGBM_greek<-function(Nsim,S0,mu,sigma,Deltat,T_remain,h){
  m=T/Deltat # number of periods
  Splush=matrix(S0+h,nrow=Nsim,ncol=m+1)
  S=matrix(S0,nrow=Nsim,ncol=m+1)
  Sminush=matrix(S0-h,nrow=Nsim,ncol=m+1)
  v= mu- (sigma^2)/2
  for(i in 1:Nsim){
    Z<-rnorm(m)
    for(j in 2:(m+1)){
      Splush[i,j]=Splush[i,j-1]*exp(v*Deltat+sigma*sqrt(Deltat)*Z[j-1])
      S[i,j]=S[i,j-1]*exp(v*Deltat+sigma*sqrt(Deltat)*Z[j-1])
      Sminush[i,j]=Sminush[i,j-1]*exp(v*Deltat+sigma*sqrt(Deltat)*Z[j-1])
    }
  }
  list(Splush=Splush,S=S,Sminush=Sminush)
}

h=S0*0.001
Nsim=10000
SimHSI<-SimGBM_greek(Nsim,S0,mu,sigma,dt,T_remain,h)
SimHSISplush<-SimHSI$Splush
SimHSIS<-SimHSI$S
SimHSISminush<-SimHSI$Sminush
SimNotesplush<-apply(SimHSISplush,1,NotePayoff)
SimNotes<-apply(SimHSIS,1,NotePayoff)
SimNotesminush<-apply(SimHSISminush,1,NotePayoff)
NoteValueplush=exp(-r*T_remain)*mean(SimNotesplush)
NoteValue=exp(-r*T_remain)*mean(SimNotes)
NoteValueminush=exp(-r*T_remain)*mean(SimNotesminush)

NoteDelta=(NoteValueplush-NoteValueminush)/(2*h); NoteDelta
NoteGamma=(NoteValueplush-2*NoteValue+NoteValueminush)/(h^2); NoteGamma
```
